A little Jump\textquotesingle{}n\textquotesingle{}Fight game, filled with open source little fighter graphics. For a school project.

\subsubsection*{\href{http://www.htw-berlin.de/}{\tt Highschool Website}}

\subsection*{History}

\paragraph*{Version 0.\+9}

Reinige die Dateien langsam und Dokumentiere

Fertige sind\+:

chat.\+cpp

choosebackground.\+cpp

choosemenu.\+cpp

\paragraph*{Version 0.\+3.\+1}

Added new Controls, you can see them by typing /controls into the chat and pressing Y for seeing the \hyperlink{class_chat}{Chat}.

Maked K\+I -\/ Harder for Players.

\paragraph*{Version 0.\+3}

Added a 4th \hyperlink{class_character}{Character} called Chenpo.

Added a Icon for the 3rd Arena (Wall Arena).

Adjusted Sound for Startscreen.

Added Image for Startscreen (+\+O\+P+ W\+I\+N\+D\+O\+W\+S P\+A\+I\+N\+T +\+O\+P+).

Implement K\+I for Player against K\+I.

Implement 2 Player \hyperlink{class_character}{Character} Menu for 2 \hyperlink{class_character}{Character} Player Mode.

Added a S\+T\+U\+N\+N\+E\+D bool for Characters that gets hitted.

Added a temporary Stun picture.

Enemy K\+I is punching!

\paragraph*{Version 0.\+2.\+2}

Added Sounds to the Startscreen, \hyperlink{class_character}{Character} Menu and Fightscreen.

Adjusted the Screen for the \hyperlink{class_character}{Character} Menu.

Added indicators for range while Punching.

\paragraph*{Version 0.\+2}

3 Characters are available now-\/

\hyperlink{class_character}{Character} icons in the fight dialog.

Included an enemy (no interactions right now).

Added get\+Name nad Get\+Icon to character class.

Added escape from fight window, so you can go to the Startmenu now.

Added Winning\+Screen.

Added Lifelosing when punching (This is at the moment global, will be fixed soon).

\paragraph*{Version 0.\+1.\+5}

Fixed Jumpingleft of all characters.

Deleted some unnecessary and unused variables.

Added Ahri as \hyperlink{class_character}{Character}.

\paragraph*{Version 0.\+1.\+4}

New \hyperlink{class_character}{Character} Added (1 and 4 can be used now).

New Icons in the Choosemenu Added.

Added Mirrored animations for the Characters by Jumping, Punching, Crouching, Standing and Walking.

\paragraph*{Version 0.\+1.\+3}

Bugfix on Windows Version.

Integrated O\+S indentificator.

The F\+P\+S will be changed now when O\+S is changing.

Implemented mirror images for left and right stand animation.

Did make the first menu button pressable for enter.

\paragraph*{Version 0.\+1.\+1}

\begin{quote}
Not fully functional version.\end{quote}
